\vspace{0.25em}

\renewcommand{\thefootnote}{\arabic{footnote}}
\setcounter{footnote}{0}

\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}

As the STEDT project was nearing the end of its 28-year run in
2014-15, we became more and more preoccupied with trying to figure out
how best to preserve and disseminate our databases and etymologies.
Obviously there would be no point in contemplating a printout of the
more than 500,000 records in our main lexical database, On the other
hand, it did not seem beyond the realm of possibility to prepare a
printed version of our nearly 6000 etymologies, presenting our
reconstructions along with their “supporting forms” from individual Tibeto-Burman languages and Chinese.

This latter idea was put forth with the greatest persuasiveness by
J.B. Lowe, who felt that the STEDT project owed it to the scholarly
community and the general public to make available a tangible snapshot
of our latest etymological thinking as the project came to a close. To
demonstrate the feasibility of this idea, J.B. contacted the UC
Berkeley Library Bindery, which produced a handsomely bound draft
version of the etymologies that came to two folio volumes totaling 1,137 pages.

Meanwhile my main concern was to revise or “rectify” all the
etymologies before they were enshrined in print, paying special
attention to the numerous weakly attested roots (“WAR’s”) among them.
I carried out this “WARfare” to the best of my ability over a period
of several months,
with the indispensable assistance of a succession of talented Stedtniks
who navigated me through the labyrinth of our lexical and etymological databases.

Finally we have had to call a halt. This printed version accurately
represents my latest thinking, but I have no illusions that every
detail of my analyses will stand the test of time. It is my hope that
some way will be found to periodically update and expand both the
electronic and printed versions of our lexical database and our
etymologies. In any case, a limited run of the present 2-volume
printed version is now available at the relatively modest price of
\$250. To order a copy, please email me at {\it matisoff@berkeley.edu}.

						United in zeal for TB/ST studies,

						James A. Matisoff
						Berkeley, June 2015
